Testing Filtering Parameters

### 2016-07-12 code/filtering.Rmd
Maybe switch it around?

```{r}
my.loess$data$smoothed <- smth.gaussian(my.loess$data$resid, window = 16)
my.inds <- which(diff(sign(diff(my.loess$data$smoothed))) == -2) + 1
my.inds2 <- which(diff(sign(diff(my.loess$data$smoothed))) == 2) + 1

>>>>

```{r}
my.loess$data$smoothed_first <- my.loess$data$resid - smth.gaussian(my.loess$data$resid, window = 16)
my.loess$data$smoothed <- my.loess$data$smoothed_first - smth.gaussian(my.loess$data$smoothed_first, window = 160)
my.inds <- which(diff(sign(diff(my.loess$data$smoothed))) == -2) + 1
my.inds2 <- which(diff(sign(diff(my.loess$data$smoothed))) == 2) + 1
